---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MToolR

<!-- badges: start -->
<!-- badges: end -->

MToolR is a companion package for the Mental Model Mapping Tool M-Tool (https://www.m-tool.org/).
The package provides:
  a) functionality to load and process data generated by M-Tool
  b) procedures for common (basic) analytical tasks
  c) visualization functions
  
⚠️ This package is literally a couple of hours old - it's under development and use it at your own peril at the moment ⚠️

## Installation

You can install the development version of MToolR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("marioangst/MToolR")
```

## Example 1: Read in .csv file exported from M-Tool, aggregate and visualize

Say you have exported a file called "test_export.csv" from M-Tool and have saved it in a folder data/. Here is how to read it into R and create a first plot for a user.

```{r example1, warning=FALSE}
library(MToolR)

mtool_data <-
  MToolR::parse_mtools_csv("data/test_export.csv", 
                           exclude_nonresponse = TRUE)

plot_user_model(mtool_data,
                user = mtool_data$User_ID[100])

```

<!-- build this with devtools::build_readme() -->
